Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-10-06 manuscript/tables&figures.Rmd
adjust Fig. 4 legend

**Figure 4. Drought resistance, $Rt$ (a), and resilience, $Rs$ (b) value ranges across species for the three focal droughts.** Species codes are given in Table 2, and closed dots represent outliers from the main boxplots. The dotted line at y=1 represents no change in $Rt$ or $Rs$ from the previous year. Letters illustrate significance groupings per year (colored and ordered, top to bottom, 1966, 1977, 1999). That is, a group of species with the same letter above their boxplot (e.g. "b") are statistically different from species in another group (e.g. "a"). Letter groupings do not transfer across variables $Rt$ and $Rs$. See Fig. S7 for parallel plot for recovery ($Rc$). Analysis conducted using *agricolae* package in R. Descriptions of variables (e.g. $ln[H]$ can be found in Table 3.

@@

![**Figure 3. Visualization of top statistical models for drought resistance ($Rt$), recovery ($Rc$), and resilience ($Rs)$ for all droughts combined and for each individual drought year.** For cases where the best model includes a DBH x TWI interaction ($Rc$ in all droughts and 1966, $Rs$ in all droughts and 1977), we plot the best model without the interaction. Visualization of the best mixed effects model per drought scenario was created by the *visreg* package in R, and confidence intervals were defined via bootsrapping in the *bootpredictlme4* package. Model coefficients are given in Tables S8 and S10-11. Descriptions of variables (e.g. $ln[H]$ can be found in Table 3.)
](tables_figures/publication/Figure3_model_vis_all.png)

@@

![**Figure 4. Drought resistance, $Rt$ (a), and resilience, $Rs$ (b) value ranges across species for the three focal droughts.** Species codes are given in Table 2, and closed dots represent outliers from the main boxplots. The dotted line at y=1 represents no change in $Rt$ or $Rs$ from the previous year. Letters illustrate significance groupings per year (colored and ordered, top to bottom, 1966, 1977, 1999). That is, a group of species with the same letter above their boxplot (e.g. "b") are statistically different from species in another group (e.g. "a"). Letter groupings do not transfer across variables $Rt$ and $Rs$. See Fig. S7 for parallel plot for recovery ($Rc$). Analysis conducted using *agricolae* package in R.](tables_figures/publication/Figure4_Rt-Rs_across_sp.png)

>>>>

**Figure 4. Drought resistance, $Rt$ (a), and resilience, $Rs$ (b) across species for the three focal droughts.** Species codes are given in Table 2. Shaded boxes represent the interquartile range, with horizontal line at median, whiskers represent the range within 2.7 SD, and dots represent outliers. The horizontal dotted line at y=1 represents no change in growth between the five years prior to drought and the drought year ($Rt$) or the five years following the drought ($Rs$). Letters illustrate significance groupings per year (colored and ordered, top to bottom, 1966, 1977, 1999). That is, a group of species with the same letter above their boxplot (e.g. "b") are statistically different from species in another group (e.g. "a"). Letter groupings do not transfer across variables $Rt$ and $Rs$. See Fig. S7 for parallel plot for recovery ($Rc$). Analysis conducted using *agricolae* package in R. Descriptions of variables (e.g. $ln[H]$) can be found in Table 3.

@@

![**Figure 3. Visualization of top statistical models for drought resistance ($Rt$), recovery ($Rc$), and resilience ($Rs)$ for all droughts combined and for each individual drought year.** For cases where the best model includes a DBH x TWI interaction ($Rc$ in all droughts and 1966, $Rs$ in all droughts and 1977), we plot the best model without the interaction. Visualization of the best mixed effects model per drought scenario was created by the *visreg* package in R, and confidence intervals were defined via bootsrapping in the *bootpredictlme4* package. Model coefficients are given in Tables S8 and S10-11. Descriptions of variables (e.g. $ln[H]$ can be found in Table 3.)](tables_figures/publication/Figure3_model_vis_all.png)

@@

![**Figure 4. Drought resistance, $Rt$ (a), and resilience, $Rs$ (b) across species for the three focal droughts.** Species codes are given in Table 2. Shaded boxes represent the interquartile range, with horizontal line at median, whiskers represent the range within 2.7 SD, and dots represent outliers. The horizontal dotted line at y=1 represents no change in growth between the five years prior to drought and the drought year ($Rt$) or the five years following the drought ($Rs$). Letters illustrate significance groupings per year (colored and ordered, top to bottom, 1966, 1977, 1999). That is, a group of species with the same letter above their boxplot (e.g. "b") are statistically different from species in another group (e.g. "a"). Letter groupings do not transfer across variables $Rt$ and $Rs$. See Fig. S7 for parallel plot for recovery ($Rc$). Analysis conducted using *agricolae* package in R. Descriptions of variables (e.g. $ln[H]$) can be found in Table 3.](tables_figures/publication/Figure4_Rt-Rs_across_sp.png)
